Quality measure notes

### 2021-08-11 StateOfPractice/Ao-Report/13Methods.tex
MI report - updates

\chapter{Research Methodology}
\label{ch_methods}

@@

Our methodology involves several steps, shown as follows:
\begin{enumerate}
\item choosing a software domain (Section \ref{sec_domain_selection});
\item collecting and filtering software packages (Section \ref{sec_software_selection});
\item grading the selected software (Section \ref{sec_grading_software});
\item interviewing development teams for further information (Section \ref{sec_interview_methods}).
\end{enumerate}

Section \ref{sec_applying_method} presents an example of how we applied the methodology on the MI domain.

@@

Before showing our filtered list to the domain experts, we ask them to list the top 10 software in the domain. Then, we cross-compare the two lists and discuss the commons and differences. We value their opinions on the filtering process. For example, if a software package is not OSS and has no updates for a long while, but the domain experts identify it as a valuable product, we still consider it to keep.

@@

\subsection{Interview Process}
\label{sec_interview_process}
Since the members of the development teams are usually around the world, we organize these interviews as virtual meetings online with \hyperlink{https://zoom.us/}{Zoom}. After receiving consent from the interviewees, we also record and transcribe our discussions.

\section{Applying the Method to MI}
\label{sec_applying_method}

Based on the principles in Section \ref{sec_domain_selection}, we selected the MI domain and the sub-group of software with the Visualization function shown in Figure \ref{fig_mi_functions}. We also included Dr. Michael Noseworthy and some of his students as the MI domain experts in our team.

By using the method in Section \ref{sec_identify_software_candidates}, we identified 48 MI software projects as the candidates from publications \cite{Bjorn2017} \cite{Bruhschwein2019} \cite{Haak2015}, online articles related to the domain \cite{Emms2019} \cite{Hasan2020} \cite{Mu2019}, forum discussions related to the domain \cite{Samala2014}, etc.

Appendix \ref{ap_list_before_filtering} shows all the 48 software packages. Our filtering process is as follows:

@@

There were 29 software products left on the list. We still preferred projects using git and GitHub and being updated recently, but did not apply this filter since packages were already below 30. Even without this filter, 27 out of the 29 software packages on the final list used git, and 24 chose GitHub.

Then we followed the steps in Section \ref{sec_grading_software} to measure and grade the software. 27 out of the 29 packages are compatible with two or three different OS such as Windows, macOS, and Linux, and 5 of them are browser-based, making them platform-independent. However, in the interest of time, we only performed the measurements for each project by installing it on one of the platforms, most likely Windows.

Before contacting any interviewee candidate, we received ethics clearance from the McMaster University Research Ethics Board (Appendix \ref{ap_ethics}). Going through the interview process in Section \ref{sec_interview_methods}, we contacted all of the 29 teams. As a result, developers/architects from 8 teams have participated in our interviews so far.

>>>>

\chapter{Methodology}
\label{ch_methods}

@@

Our method involves several steps, shown as follows:
\begin{enumerate}
\item choosing a software domain (Section \ref{sec_domain_selection});
\item collecting and filtering software packages (Section \ref{sec_software_selection});
\item grading the selected software (Section \ref{sec_grading_software});
\item interviewing development teams for further information (Section \ref{sec_interview_methods}).
\end{enumerate}

Section \ref{sec_applying_method} presents an example of how we applied the method on the MI domain.

@@

\subsection{Vet the Software List}
\label{sec_vet_software_list}
Before showing our filtered list to the domain experts, we ask them to list the top 10 software in the domain. Then, we cross-compare the two lists and discuss the commons and differences.  In addition, we ask them to vet our filtered list. They provide opinions on whether the list is reasonable to them. We also value their opinions on the filtering process. For example, if a software package is not OSS and has no updates for a long while, but the domain experts identify it as a valuable product, we still consider it to keep.

@@

\subsection{Interview Process}
\label{sec_interview_process}
Before contacting any interviewee candidate, we need to receive ethics clearance from the McMaster University Research Ethics Board. Since the members of the development teams are usually around the world, we organize these interviews as virtual meetings online with \hyperlink{https://zoom.us/}{Zoom}. After receiving consent from the interviewees, we also record and transcribe our discussions.

\section{Applying the Method to MI}
\label{sec_applying_method}
This section shows an overview of applying our method to the MI domain.

\subsection{Domain Selection}
Based on the principles in Section \ref{sec_domain_selection}, we selected the MI domain and the sub-group of software with the Visualization function shown in Figure \ref{fig_mi_functions}. We also included Dr. Michael Noseworthy and some of his students as the MI domain experts in our team.

\subsection{Software Product Selection}
By using the method in Section \ref{sec_identify_software_candidates}, we identified 48 MI software projects as the candidates from publications \cite{Bjorn2017} \cite{Bruhschwein2019} \cite{Haak2015}, online articles related to the domain \cite{Emms2019} \cite{Hasan2020} \cite{Mu2019}, forum discussions related to the domain \cite{Samala2014}, etc. Appendix \ref{ap_list_before_filtering} shows all the 48 software packages.

Guided by the method in Section \ref{sec_filter_software_list}, we filtered the list with a process as follows:

@@

We still preferred projects using git and GitHub and being updated recently, but did not apply this filter since packages were already below 30. Even without this filter, 27 out of the 29 software packages on the filtered list used git, and 24 chose GitHub.

Following the process in Section \ref{sec_vet_software_list}, our domain experts provided a list of top software that contains 12 software products (Table \ref{tab_top_software_experts}). We compared two lists and found six common ones. We did not include the rest in our final list, because their major function was not Visualization.

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Software & On both lists \\ \hline
3D Slicer & X \\
Horos & X \\
ImageJ & X \\
Fiji & X \\
AFNI &  \\
FSL &  \\
Freesurfer &  \\
Mricron & X \\
Mango & X \\
Tarquin &  \\
Diffusion Toolkit &  \\
MRItrix &  \\ \hline
\end{tabular}
\caption{\label{tab_top_software_experts}Top software by the MI domain experts}
\end{table}

We included \textit{Mango} in the initial list, but removed it because it was not OSS. However, we kept \textit{Papaya}, a the web version of \textit{Mango}. Instead of \textit{MRIcron}, we chose \textit{MRIcroGL}, because \textit{MRIcron} development had moved to
\textit{MRIcroGL} \cite{Rorden2021b}.

After vetting our filtered list, the domain experts believed it was reasonable and did not identify any problem. Thus, as shown in Appendix \ref{ap_list_before_filtering}, eventually we had 29 software products on the final list.

\subsection{Grading Software}
Then we followed the steps in Section \ref{sec_grading_software} to measure and grade the software. 27 out of the 29 packages are compatible with two or three different OS such as Windows, macOS, and Linux, and 5 of them are browser-based, making them platform-independent. However, in the interest of time, we only performed the measurements for each project by installing it on one of the platforms, most likely Windows.

\subsection{Interviews}
We received ethics clearance from the McMaster University Research Ethics Board (Appendix \ref{ap_ethics}). Going through the interview process in Section \ref{sec_interview_methods}, we contacted all of the 29 teams. As a result, developers/architects from 8 teams have participated in our interviews so far.

### 2021-08-11 StateOfPractice/Ao-Report/14MeasurementResults.tex
MI report - minor updates
MI report - updates

This section shows the summary of the measurement results. The detailed data can be found in the repository \hyperlink{https://github.com/smiths/AIMSS}{https://github.com/smiths/AIMSS}.

Table \ref{tab_final_list} shows the 29 software packages that we measured. We tried to find the initial release dates (Rlsd) in the documents, such as the introduction and release notes. We did not find this date for two projects and marked them with ``?". We used the date of the latest change to each code repository to decide the latest update. We found out funding information (Fnd) for eight projects, and we are not sure about the rest.

>>>>

As discussed in Section \ref{sec_applying_method}, we applied our method to the MI domain. This section shows the summary of the measurement results. The detailed data can be found in the repository \hyperlink{https://data.mendeley.com/datasets/k3pcdvdzj2/1}{https://data.mendeley.com/datasets/k3pcdvdzj2/1}.

Table \ref{tab_final_list} shows the 29 software packages that we measured. We found the initial release dates (Rlsd) in their documents for most projects and marked the rest two with ``?". We used the date of the latest change to each code repository to decide the latest update. We found out funding information (Fnd) for only eight projects.

### 2021-08-11 StateOfPractice/Ao-Report/15InterviewsWithDevelopers.tex
MI report - updates

This section summarizes some answers from the interviews with developers. We interviewed nine developers from eight of the 29 MI software projects. The eight projects are \textit{3D Slicer}, \textit{INVESALIUS 3}, \textit{dwv}, \textit{BioImage Suite Web}, \textit{ITK-SNAP}, \textit{MRIcroGL}, \textit{Weasis}, and \textit{OHIF}. We spent about 90 minutes for each interview and asked 20 prepared questions. We also asked following-up questions when we thought it was worth diving deeper. One participant was too busy to have an interview, so they wrote down their answers.

In this section, we only discuss the answers that we think are the most exciting and essential. We summarize the rest of the interviews in Appendix \ref{ap_interview}. The interviewees may have provided multiple answers to each question. When counting the number of interviewees for each response, we count every interviewee with this answer.

>>>>

We applied our method to the MI domain (Section \ref{sec_applying_method}) and summarize some answers from the interviews with developers in this section. We only discuss the answers that we think are the most exciting and essential in this section, and summarize the rest in Appendix \ref{ap_interview}.

We interviewed nine developers from eight of the 29 MI software projects. The eight projects are \textit{3D Slicer}, \textit{INVESALIUS 3}, \textit{dwv}, \textit{BioImage Suite Web}, \textit{ITK-SNAP}, \textit{MRIcroGL}, \textit{Weasis}, and \textit{OHIF}. We spent about 90 minutes for each interview and asked 20 prepared questions. We also asked following-up questions when we thought it was worth diving deeper. One participant was too busy to have an interview, so they wrote down their answers. The interviewees may have provided multiple answers to each question. Thus, when counting the number of answers, the total result can be larger than nine.
